Code Overflow: \\ An empirical study of online code reuse

### 2016-08-14 latex/stackoverflow.tex
Many changes. Added new results after fixing comment problems

Manual investigation of Simian's clone report showed that there were problematic fragments (6 for defaults, 0 for FSE'13, and 11 for CloPlag). These fragments generate false clone containing array initialisation. Hence, they were removed from the result set before analysis.

\begin{table*}[h]
	\centering
	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c}{Simian FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total & 647 & 24,802 & -- & -- &  152 & 7,289,272 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
		Mean & -- & 38 & 7.53 & 0.27 & -- & 47,956 & 4.76 & 0.27 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ % & -- & 9,356 & 4.74 & 0.26 \\
		Std Dev. & -- & 87 & 3.87 & 0.22 & -- & 433,467 & 0.93 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\ % & -- & 96,038	& 0.99 & 0.18 \\
		Max & -- & 551 & 63 & 0.94 & -- & 5,278,408 & 8 & 0.83 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ % & -- & 7,837,204 & 28 & 0.94 \\
		Min & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.01 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
		Median & -- & 3 & 7 & 0.22 & -- & 22.5 & 4 & 0.23 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ % & -- & 27 & 4 & 0.22 \\
		Mode & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ % & -- & 1 & 4 & 0.50 \\
		\hline
	\end{tabular} %
}
\end{table*}

@@

\begin{table}[h]
	\centering
	\caption{63 Qualitas projects (new versions checked on 2016-08-05)}
	\label{t:new_and_old}
\begin{tabular}{l|r|r|l}
	\hline 
	Projects & Old version & New versions & License \\
	\hline
	ArgoUML & 0.34 & \\
	Compiere & 330 & \\
	FitLibrary20100806 & & \\
	JGroups & 2 & \\
	Vuze & 4812 & \\
	antlr & 4-4.0 & \\
	aoisrc & 281 & \\
	apache-ant & 1.8.4 & \\
	aspectj & 1.6.9 & \\
	axion & 1.0-M2 & \\
	batik & 1.7 & \\
	c-jdbc & 2 & \\
	castor & 1 & \\
	cayenne & 3 & \\
	checkstyle & 5 & \\
	cobertura & 1 & \\
	colt & 1 & \\
	columba & 1 & \\
	commons-collections & 3 & \\
	db-derby & 10 & \\
	displaytag & 1 & \\
	drawswf & 1 & \\
	drjava & 20100913-r5387-src & \\
	eXoPortal & v1 & \\
	emma & 2 & \\
	findbugs & 1 & \\
	fit-java & 1 & \\
	freecol & 0 & \\
	freecs & 1 & \\
	freemind & 0 & \\
	galleon & 2 & \\
	ganttproject & 2 & \\
	geotools & 2 & \\
	hadoop & 1 & \\
	heritrix & 1 & \\
	hibernate & release-4 & \\
	hsqldb & 2 & \\
	htmlunit & 2 & \\
	iReport & 3 & \\
	iText & 5 & \\
	informa & 0 & \\
	ivatagroupware & 0 & \\
	jFin DateMath & R1\_0\_1 & \\
	jOggPlayer & 114s & \\
	jag & 6 & \\
	james & 2 & \\
	jasml & 0 & \\
	jasperreports & 3 & \\
	javacc & 5 & \\
	jboss & 5 & \\
	jchempaint & 3 & \\
	jedit & 4 & \\
	jena & 2 & \\
	jext & 5 & \\
	jfreechart & 1 & \\
	jgraph & latest-bsd & \\
	jgraphpad & 5 & \\
	jgrapht & 0 & \\
	jmoney & 0 & \\
	jparse & & \\
	jpf & 1 & \\
	junit & 4 & \\
	shiftone-jrat & 0 & \\
	\hline 
\end{tabular} 
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{18 agreed good-match(0.7) cloned pairs between Simian and Nicad (14 are unique)}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 1 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 3 & 5 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[H]
	\centering
	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
	\label{t_dup_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 9 & 3 & 0 & 0 \\%      & 709             \\
		$S_dN_f$ & 3 & 3 & 0 & 0 \\ % & 4680            \\
		$S_fN_d$ & 0 & 0 & 1 & 1 \\
		$S_fN_f$ & 0 & 0 & 1 & 5 \\	
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings  (510 are unique)}
	\label{t_dup_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 373 & 17 & 0 & 0 \\%      & 709             \\
		$S_dN_f$ & 17 & 118 & 0 & 0 \\ % & 4680            \\
		$S_fN_d$ & 0 & 0 & 1 & 1 \\
		$S_fN_f$ & 0 & 0 & 1 & 36 \\	
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
	\label{tab:search}
	\begin{tabular}{l|r|r}
		\hline 
		Settings & Found & Not found \\ 
		\hline 
		Simian$_{df}$  &  40 & 1* \\ 
		\hline 
		Simian$_{fse13}$ & 0 & 41  \\ 
		\hline 
		NiCad$_{df}$  & 9 & 32 \\ 
		\hline 
		NiCad$_{fse13}$ &  9 & 32 \\ 
		\hline 
	\end{tabular} 
\end{table}

>>>>

Manual investigation of Simian's clone report showed that there were problematic 11 fragments. These fragments generate false clone containing array initialisation. Hence, they were removed from the result set before analysis.

\begin{table*}[h]
	\centering
	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
	\label{t_simian_raw_results}
	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{Statistics} 
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c|}{Simian FSE'13 settings}
		& \multicolumn{4}{c|}{Simian Default settings} 
		& \multicolumn{4}{c}{Simian FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=5}  
		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
		& \multicolumn{4}{c|}{rename=none,abstract=none} 
		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total  	& 654 	& 24,929 	& -- 	& --	& 1,175 & 16,957,362 & --	& --	& 985 	& 105,118 	& --	& --	& 12,084	& 113,557,298 & --		& -- \\
		Mean  	& --	& 38 		& 7.54 	& 0.27 	& --	& 14,444 	& 4.80 	& 0.28 	& --	& 107 		& 9.52 	& 0.25 	& -- 		& 9,397 	& 5.21 		& 0.20 \\
		Std Dev. & --  	& 87 		& 3.21 	& 0.22 	& --	& 281,747 	& 1.22 	& 0.18 	& --	& 198 		& 3.07 	& 0.18 	& --		& 12,098 	& 1.73 		& 0.16 \\
		Max  	& --	& 551 		& 49.00 & 0.94 	& --	& 9,599,676 & 18.00 & 0.89 	& --	& 1,792 	& 39.00 & 0.80 	& --		& 227,077 	& 44.00 	& 0.86 \\
		Min  	& --	& 1 		& 5.00 	& 0.01 	& --	& 1 		& 4.00 	& 0.02 	& --	& 1 		& 7.00 	& 0.02 	& --		& 1 		& 3.00 		& 0.01 \\
		Median  & --	& 3 		& 7.00 	& 0.23 	& --	& 22 		& 5.00 & 0.24 	& --	& 15 		& 8.00 	& 0.19 	& --		& 6,105 	& 5.00 		& 0.15 \\
		Mode  	& --	& 1 		& 7.00 	& 0.25 	& --	& 1 		& 4.00 	& 0.50 	& --	& 1 		& 8.00 	& 0.53 	& --		& 1 		& 4.00 		& 0.33 \\
		\hline
	\end{tabular} %
}
\end{table*}

@@

\begin{table}[H]
	\centering
	\caption{63 Qualitas projects (new versions checked on 2016-08-05)}
	\label{t:new_and_old}
\begin{tabular}{l|r|r|c|p{5cm}|p{3cm}}
	\hline 
	Projects & Old version & New versions & Latest change & License & Notes \\
	\hline
	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 & Eclipse Public License v.1.0 \\
	Compiere & 330 & -- & 01/06/2010 &  GNU General Public License v.2.0 & No longer OSS \\
	FitLibrary & 20100806 & 20111026 & 12/07/2014 & GNU General Public License v.2.0 \\
	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016  & Apache License, v.2.0 \\
	Vuze & 4812 & 5721-20 & 12/05/2016 & GNU General Public License v.2.0 &  \\
	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & BSD License \\
	aoisrc & 281 & 302 & 12/01/2015 &  GNU General Public License v.2.0 \\
	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & Apache License, v.2.0 \\
	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & Eclipse Public License 1.0 \\
	axion & 1.0-M2 & -- & 08/03/2013 & Proprietary (BSD/Apache-style) \\
	batik & 1.7 & 1.8 & 16/03/2015 & Apache License, v.2.0 \\
	c-jdbc & 2.0.2 & -- & 16/09/2005 & GNU Lesser General Public License, v.2.1 \\
	castor & 1.3.1 & 1.4.2 & 20/06/2016 & Apache License, v.2.0 \\
	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & Apache License, v.2.0 \\
	checkstyle & 5.1 & 7.2  & 04/08/2016 & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & GNU General Public License v.2.0  \\
	colt & 1.2.0 & -- & 09/09/2014 &  Proprietary (CERN) \\
	columba & 1.4 & -- & 20/04/2007 & Mozilla Public License 1.1  \\
	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & Apache License, v.2.0 \\
	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & Apache License, v.2.0 \\
	displaytag & 1.2 & 2.0 & 17/08/2014 & MIT License \\
	drawswf & 1.2.9 & -- & 02/04/2013 & GNU General Public License v.2.0 \\
	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & BSD License \\
	eXoPortal & ??? & 4.4 & 24/06/2016 & GNU Lesser General Public License v.3.0 \& proprietary \\
	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & Common Public License 1.0 \\
	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & GNU Lesser General Public License, v.2.0 \\
	fit-java & 1.1 & -- & 04/06/2013 & GNU General Public License v.2.0 \\
	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & GNU General Public License v.2.0 &  \\
	freecs & 1.3.20100406 & -- & 22/04/2013 & GNU General Public License v.3.0 &   \\
	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & GNU General Public License v.2.0+ &  \\
	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & GNU General Public License v.2.0 \\
	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & GNU General Public License v.3.0 &  \\
	geotools & 2.7-M3 & 16 & 02/08/2016 & GNU Lesser General Public License, v.2.0 \\
	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & Apache License, v.2.0 \\
	heritrix & 1.14.4 & -- & 05/06/2013 & GNU Lesser General Public License, v.2.1 \\
	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & GNU Lesser General Public License, v.2.1+ \\
	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & BSD License \\
	htmlunit & 2.8 & 2.24 & 27/07/2016 & Apache License, v.2.0 \\
	iReport & 3.7.5 & -- & 28/05/2014 & Affero GNU Public License, v.3.0 \\
	iText & 5.0.3 & 7.0.0 & 02/05/2016 & Affero GNU Public License, v.3.0 \\
	informa & 0.7.0-alpha2 & -- & 07/11/2008 & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
	ivatagroupware & 0.11.3 & -- & 27/02/2013  & GNU General Public License v.2.0 \\
	jFin DateMath & R1\_0\_1 & -- & 25/04/2013  & GNU General Public License v.2.0 \\
	jOggPlayer & 114s & -- &  15/04/2013   & GNU General Public License v.2.0 \\
	jag & 6.1 & 6.2 & 08/04/2013   & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries they use. \\
	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & Apache License, v.2.0 \\
	jasml & 0.10 & -- & 08/03/2013 & Apache Software License \\
	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & GNU Lesser General Public License, v.3.0 &  \\
	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & Proprietary (Sun) \\
	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & GNU Lesser General Public License, v.2.1 & It is renamed to Wildfly. \\
	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & GNU Lesser General Public License, v.2.1+ &  \\
	jedit & 4.3.2 & 5.3.0 & 20/10/2015  & GNU General Public License v.2.0 &  \\
	jena & 2.6.3 & 3.1.0 & 10/05/2016 & Apache License, v.2.0 \\
	jext & 5.0 & -- & 18/08/2004   & GNU General Public License v.2.0 &  \\
	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016  & GNU Lesser General Public License, v.2.0 &   \\
	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & Proprietary (mxGraph License) \\
	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
	jmoney & 0.4.4 & -- & 17/04/2016 & GNU General Public License v.2.0 &  \\
	jparse & 0.96 & -- & 29/07/2004 & GNU Lesser General Public License, v.2.1 \\
	jpf & 1.5.1 & ??? & 13/01/2012 & Apache License, v.2.0 \\
	junit & 4.11 & 4.12 & 04/12/2014 & Eclipse Public License, v.1.0 \\
	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & GNU Lesser General Public License, v.2.0 &  \\
	\hline 
\end{tabular} 
\end{table}

@@

However, for the 2 NiCad settings, we found some renaming and clustering errors which resulted in fewer projects having clone reports. For NiCad default settings, 6 projects had clustering failed errors: \textit{cayenne,checkstyle, db-derby, geotools, hibernate, iReport}. For NiCad FSE13 settings, 4 projects had renaming failed errors: \textit{Vuze, aspectj, eXoPortal, hibernate} and 13 projects had clustering failed errors: \textit{ArgoUML, castor, cayenne, checkstyle, db-derby, drjava, ganttproject, geotools, iReport, ivatagroupware, jasperreports, jboss, jchempaint} as depicted in Table \ref{tab:projects_missing}. So these projects are also missing from agreed clone pairs.

\begin{table}[h]
	\centering
	\caption{Qualitas projects successfully analysed by Simian and NiCad}
	\label{tab:projects_missing}
	\begin{tabular}{r|r|r|r}
		\hline
		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
		63	& 57 & 63 & 46 \\
		\hline
		& \textit{6 clustering failed} &  & \textit{13 clustering failed} \\
		\hline
		& cayenne   &	& cayenne \\
		& checkstyle &  & checkstyle \\
		& db-derby 	& & db-derby \\
		& geotools 	& & geotools \\
		& iReport 	& & iReport \\
		& hibernate & & ArgoUML \\
		&			& & castor \\
		&			& & drjava \\
		&			& & ganttproject \\
		&			& & ivatagroupware \\
		&			& & jasperreports \\
		&			& & jboss \\
		&			& & jchempaint \\
		\hline
		& \textit{renaming failed} & &  \textit{4 renaming failed} \\
		\hline
		&			& & Vuze \\
		&			& & aspectj \\
		&			& & eXoPortal \\
		&			& &  hibernate \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{1,415 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,406 are unique)}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 6 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 12 & 1388 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

%\begin{table}[H]
%	\centering
%	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
%	\label{t_dup_agreed_good_clone_pairs}
%	\begin{tabular}{l|r|r|r|r}
%		\hline
%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
%		\hline
%		$S_dN_d$ & 9 &    &   &      \\%      & 709             \\
%		$S_dN_f$ & 9 & 12 &   &      \\ % & 4680            \\
%		$S_fN_d$ & 0 & 0  & 6 &      \\
%		$S_fN_f$ & 0 & 0  & 0 & 1388 \\	
%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
%		\hline
%	\end{tabular}
%\end{table}

@@

\begin{table}[h]
	\centering
	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
	\label{t_dup_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r|r|r|r}
		\hline
		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
		\hline
		Total 	 & 481  & 418	& 60	& 10,206	& \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

@@

\begin{table}[H]
	\centering
	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
	\label{tab:search}
	\begin{tabular}{l|r|r}
		\hline 
		Settings & Found & Not found \\ 
		\hline 
		Simian$_{df}$  &  40 & 1* \\ 
		\hline 
		Simian$_{fse13}$ & 0 & 41  \\ 
		\hline 
		NiCad$_{df}$  & 17 & 24 \\ 
		\hline 
		NiCad$_{fse13}$ &  24 & 17 \\ 
		\hline 
	\end{tabular} 
\end{table}
